---
title: "Tidy Tuesday #2"
author: "Tiffany Wibisono"
date: '2022-05-11'
output: 
  html_document:
  toc: TRUE
  toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidytuesdayR)
library(tidyverse)
library(vtable)


nyt_titles <- readr::read_tsv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-05-10/nyt_titles.tsv')

nyt_full <- readr::read_tsv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-05-10/nyt_full.tsv')

```

1. Top 3 author in NY Best Seller based on the number of occurrence
```{r}
top3Author = nyt_titles %>%
  count(author) %>%
  arrange(desc(n)) %>%
  head(3)
```
2. Danielle Steel number of books published each year
```{r}
DSteel = filter(nyt_titles, author == "Danielle Steel")
year_DS = DSteel %>%
  count(year) %>%
  rename("Danielle Steel" = "n") %>%
  arrange(desc(year)) %>%
  head(11)
```
3. Stuart Woods number of books published each year
```{r}
SWoods = filter(nyt_titles, author == "Stuart Woods")
year_SW = SWoods %>%
  count(year) %>%
  rename("Stuart Woods" = "n") %>%
  arrange(desc(year)) %>%
  head(11)
```
4. Stephen King number of books published each year
 Graph
```{r}
SKing = filter(nyt_titles, author == "Stephen King")
year_SK = SKing %>%
  count(year) %>%
  rename("Stephen King" = "n") %>%
  arrange(desc(year)) %>%
  head(10)
```
5. Merge 
```{r}
listLastTenYears = list(year_DS, year_SK, year_SW)
lastTenYears = listLastTenYears%>%
  reduce(full_join, by = "year")
```
5. Graph
```{r}
lastTenYears %>%
  pivot_longer(cols = c("Danielle Steel", "Stuart Woods", "Stephen King")) %>%
ggplot( aes(x = year, y = value, color = name)) + labs(x = "Year", y = "No. of Books Published Per Year", title = "Number Of Books Published Each Year Based on Top 3 Authors") + scale_x_continuous(breaks = 2010:2020) + geom_line()
```

The line graph explains the number of books published within the past 10 years based on the top 3 authors. From the given graph, we can see that Danielle Steel's book had the most number of books awarded by NYT Best Sellers, followed by Stuart Woods and Stephen King.