---
title: 'Week 4 Homework: College Expenses EDA'
author: "Tiffany Wibisono"
date: '2022-04-27'
output: 
  html_document:
  toc: TRUE
  toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(vtable)
library(tidyverse)
library(ggplot2)
library(scales)

data = readRDS('data/college_expenses_and_enrollment.Rdata')

vtable::vtable(data)
sumtable(data)
str(data)
```
# 1. Top 3 College Type
#### I used the count() function to count the number of different college types. Then, I arranged the the result in descending order, and used the head() function to only show the top 3 results. Afterwards, I presented this data in a bar chart using geom_col().

#### The result shows that the most popular college type is Private NP 4-Year, followed by Public 2-Year and Public 4-Year.
```{r}
Count_College_Type = data %>%
  count(type) %>%
  arrange(desc(n)) %>%
  head(3)

ggplot(Count_College_Type, aes(x = type, y = n)) + geom_col()
```

# 2. Private NP 4-Year Data
#### I used the most popular college type to do further analysis. From the result in #1, most colleges are catagorized as Private NP 4-Year; therefore, I used the filter() function to filter all rows that contain Private NP 4-Year.
```{r}
Private_NP_4Year_Data = data %>%
  filter(type == 'Private NP 4-Year')
```
# 3. Summary of Private NP 4-Year Data
#### I made use of the summary() function to create a summary of the Private NP 4-Year data.
```{r}
summary(Private_NP_4Year_Data)
```



# FINAL DRAFT: Average Expenses in Private NP 4-Year College
#### I'm using the summary data from #3 to create a a pie chart for different types of average expenses made by Private NP 4-Year colleges. In the pie chart, I inluded colors, percentage labels, and legend to make the chart more presentable.

##### Findings: Most of the expenses comes from instruction, and the least comes from public service.

```{r}
mean_research = mean(Private_NP_4Year_Data$Research)
mean_research

mean_public_service = mean(Private_NP_4Year_Data$Public.Service)
mean_public_service

mean_student_services = mean(Private_NP_4Year_Data$Student.Services)
mean_student_services

mean_instruction = mean(Private_NP_4Year_Data$Instruction)
mean_instruction

mean_academic_support = mean(Private_NP_4Year_Data$Academic.Support)
mean_academic_support

mean_other = mean(Private_NP_4Year_Data$Other)
mean_other

mean_expenses = c(13119773, 1780340, 10255967,38335587, 9948486, 31769436)
types_of_expenses = c("Research", "Public Service", "Student Services", "Instruction", "Academic Support", "Other")
percentage_expenses = round(100*mean_expenses/sum(mean_expenses), 1)
expenses_data = data.frame(percentage_expenses, types_of_expenses)

ggplot(expenses_data, aes(x = "", y = percentage_expenses, fill = types_of_expenses)) + 
  ggtitle("Private NP 4-Year Average Expenses Distribution") +
  geom_col(color = "black") + 
  geom_text(aes(label = paste(percentage_expenses, "%")),
            position = position_stack(vjust = 0.5)) +
  coord_polar(theta = "y")
```
